### 2019-11-26 report/02-methods.Rmd
Test w/wht ANG + statistical averaging

habitat_pressure %>%
  select(station, width_river_mean:temperature) %>%
  gather(env_var, value, width_river_mean:temperature) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(facets = ~ env_var, ncol = 3, scales = "free")
```

>>>>

dist_env <- habitat_pressure %>%
  select(station, width_river_mean:temperature) %>%
  gather(env_var, value, width_river_mean:temperature) 
med_dist_env <- dist_env %>%
  group_by(env_var) %>%
  summarise(value = median(value, na.rm = TRUE))

dist_env %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  geom_vline(data = med_dist_env, aes(xintercept = value), color = "red", size =
    2) +
  facet_wrap(facets = ~ env_var, ncol = 3, scales = "free")

### 2019-11-26 report/05-stability.Rmd
Test w/wht ANG + statistical averaging

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
```
```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))

@@

plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)

@@

plot_grid(plotlist = mult_plot_stab_div_bin)

@@

@@

```{r}
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))

```{r}
sync_com_troph <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  rename(species = sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(cv_bm_div_troph_grp, by = c("station", "troph_group"))
```

```{r}
sync_com_troph %>%
  filter(troph_group != 1) %>%
  select(station, troph_group, cv_com, troph_sp_nb_med) %>%
  ggplot(aes(x = troph_sp_nb_med, y = 1/cv_com, color = troph_group)) +
  geom_point() +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

@@

```{r}
sync_com_troph %>%
  unnest(contrib) %>%
  group_by(troph_group, species) %>%
  summarise(
    sum_cbt_cv_com = sum(abs(cbt_cv_com)),
    sum_cbt_cv_sp = sum(abs(cbt_cv_sp)),
    sum_cbt_sync = sum(abs(cbt_sync))
    ) %>%
  arrange(desc(sum_cbt_cv_com)) %>%
  slice(1:10) %>%
  gather(comp, contrib, sum_cbt_cv_com:sum_cbt_sync) %>%
  ggplot(aes(y = contrib, x = species)) +
  geom_point() +
  facet_grid(rows = vars(comp), cols = vars(troph_group), scales = "free_y")
```

@@

  var_cbt %<>%
    nest() %>%
    mutate(plot = map2(data, troph_group, function(.data, m_title){
	.data %>%
	ggplot(aes(y = contrib, x = div_st)) +
	  geom_point() +
	  scale_x_log10() +
	  facet_wrap(facets = ~comp, scales = "free_y") +
	  labs(title = paste0(m_title))
}
    )
    )

@@

@@

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
  arrange(cv_com)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate( troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
```

```{r}
st_basin <- get_basin_station() 
myload(region_polygon, dir = mypath("data"))
stab_div_basin <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  select(station, troph_group, biomass_stab, richness_avg) %>%
  left_join(st_basin, by = "station") %>%
  filter(!is.na(basin))

@@

plot_grid(p_stab_div_basin, p_stab_div_tot, nrow = 2)
```

@@

plot_grid(plotlist = mult_plot_stab_div_bin)
```

The relationship between stability and species diversity (Figure
\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
place where the ANG is the most present. The ANG were effectively more abundant
in the latter station (Figure: \@ref(fig:ang-map-bio)).

```{r ang-map-bio}
ang_bm <- network_analysis %>%
  left_join(select(op_analysis, opcod, station), by = "opcod") %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  filter(species == "ANG") %>%
  group_by(station) %>%
  summarise(biomass = mean(biomass))

mult_plot_ang_env <- map(env, function(x) {

  habitat_pressure$env <- habitat_pressure[[x]]

  ang_bm %>%
    left_join(habitat_pressure[, c("station", "env")], by = "station") %>%
    ggplot(aes(x = env, y = biomass)) +
    geom_point() +
    stat_poly_eq(
      formula = y ~ x,
      eq.with.lhs = "italic(hat(y))~`=`~",
      aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
      parse = TRUE) +
    geom_smooth(method = "loess", formula = y ~ x) +
    scale_y_log10() +
    labs(x = x, y = "Average biomass of ANG (g)")

  })
plot_grid(plotlist = mult_plot_ang_env)
```

@@

```{r}
cv_bm_div_troph_grp <- temporal_network_metrics_classes %>% 
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  rename(bm_st = biomass_avg, div_st = richness_avg, cv_st = biomass_cv) %>%
  mutate(troph_group = as.factor(troph_group))
```

```{r}
sync_com_troph_without_ang <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  rename(species = sp_class) %>%
  mutate(ang_logic = ifelse(!is.na(str_match(species, "ANG")[,1] == "ANG"),
      TRUE, FALSE)) %>%
  filter(troph_group != 1, ang_logic != TRUE) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(stab_div_basin, by = c("station", "troph_group"))
```

```{r stab-ang}
sync_com_troph_without_ang %>%
  mutate(stab_without_ang = 1/cv_com) %>%
  rename(stab_with_ang = biomass_stab) %>%
  filter(troph_group != 1) %>%
  select(station, troph_group, richness_avg, stab_with_ang, stab_without_ang) %>% 
  gather(stab_type, stab, stab_with_ang, stab_without_ang) %>%
  ggplot(aes(x = richness_avg, y = stab, color = troph_group)) +
  geom_point() +
  facet_grid(cols = vars(stab_type)) +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic level"
    )
```

@@

```{r}
sync_com_troph <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  select(-sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(opcod, troph_group, species) %>%
  summarise(
    troph_level = sum(troph_level * biomass /sum(biomass)),
    biomass = sum(biomass)
  ) %>%
  group_by(troph_group) %>%
  nest() %>%
  mutate(sync = map(data, ~get_sync_cv_mat(com_analysis = .x, op_analysis = op_analysis))) %>%
  unnest(sync) %>%
  mutate(sdt.dev = map_dbl(cov_mat, ~sqrt(sum(.x)))) %>%
  mutate(
    contrib = purrr::pmap(
      list(mat = com_mat, cv_com_tot = cv_com, cv_sp_tot = cv_sp, sync_tot = synchrony),
      ~compute_sp_contrib(mat = ..1, cv_com_tot = ..2, cv_sp_tot = ..3, sync_tot = ..4)),
    troph_sp_nb_med = map_dbl(com_mat, ~rowSums(.x != 0) %>% median),
    troph_sp_nb_avg = map_dbl(com_mat, ~rowSums(.x != 0) %>% mean)
      ) %>% 
  select(troph_group, station, synchrony, cv_sp, cv_com, sdt.dev, contrib,
    troph_sp_nb_avg, troph_sp_nb_med) %>%
  left_join(select(temporal_community_metrics, station, richness_avg,
      biomass_avg), by = "station") %>%
  rename(bm_st = biomass_avg, div_st = richness_avg)
```

@@

```{r cbt-top, fig.cap = "Contribution of species to the different facets of stability. Positive contribution values mean that the species contributes negatively to the metric."}
top_contrib_sp <- sync_com_troph %>%
  unnest(contrib) %>%
  group_by(station, troph_group) %>%
  mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
  group_by(troph_group, species) %>%
  summarise(
    avg_cbt_cv_com_n = mean(cbt_cv_com_n),
    avg_cbt_cv_com = mean(cbt_cv_com),
    avg_cbt_cv_sp = mean(cbt_cv_sp),
    avg_cbt_sync = mean(cbt_sync),
    avg_abs_cbt_cv_com = mean(abs(cbt_cv_com))
    ) %>%
  arrange(desc(abs(avg_cbt_cv_com_n))) %>%
  slice(1:10)

p_top_contrib_sp <- map(c(2, 3), function(x){

  mask <- top_contrib_sp$troph_group == x 
  top_sp <- unique(top_contrib_sp[mask,]$species)

  sync_com_troph %>%
    unnest(contrib) %>%
    group_by(station, troph_group) %>%
    mutate(cbt_cv_com_n = cbt_cv_com / sd(cbt_cv_com)) %>%
    filter(species %in% top_sp, troph_group == x) %>%
    gather(comp, contrib, cbt_cv_com_n, cbt_cv_com:cbt_sync) %>%
    ggplot(aes(y = contrib, x = species)) +
    geom_violin() +
    facet_grid(rows = vars(comp), scales = "free_y") +
    labs(title = x)
    })
plot_grid(plotlist = p_top_contrib_sp)
```

The figure \@ref(fig:cbt-top), left panel) shows that for the trophic group 2, LOF, GOU and
VAI were the species that contributes the most to the the CV of the community
and to its components (CVsp and synchrony). For the 3 trophic group (Figure
\@ref(fig:cbt-top), right panel), the ANG and CHE contribute the most to
stability and its facets. Interestingly, the contribution of the species to
the community CV were quite asymetric toward positive values, meaning that
species tend to stabilize more than destabilize communities.

@@

  var_cbt %<>%
    nest() %>%
    mutate(plot = map2(data, troph_group, function(.data, m_title){
	.data %>%
	ggplot(aes(y = contrib, x = div_st)) +
	  geom_point() +
	  scale_x_log10() +
	  facet_grid(rows = vars(comp), scales = "free_y") +
	  labs(title = paste0(m_title))
}
    )
    )

@@

#### Statistical averaging

```{r}
pielou <- network_analysis %>%
  select(opcod, composition) %>%
  unnest(composition) %>%
  mutate(species = str_extract(sp_class, "[A-Z]{1,3}")) %>%
  select(-sp_class) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  group_by(opcod, troph_group, species) %>%
  summarise(
    troph_level = sum(troph_level * biomass /sum(biomass)),
    biomass = sum(biomass)
  ) %>%
  group_by(troph_group, opcod) %>%
  mutate(rel_bm = biomass / sum(biomass)) %>%
  summarise(
    richness = n(),
    shannon = diversity(biomass, index = "shannon"),
    pielou = shannon / log(n())
  )

pielou %>%
  left_join(select(op_analysis, station, opcod), by = "opcod") %>%
  group_by(station, troph_group) %>%
  summarise(richness_avg = mean(richness), pielou_med = median(pielou)) %>%
  ggplot(aes(x = richness_avg, y = pielou_med)) +
  geom_point() +
  facet_grid(~troph_group)

@@

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis) %>%
  arrange(cv_com)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))
